Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-26 Papers/ms.tex
SIE mass

>>>>

The masses of the smooth and substructure components of the lens are usually
of interest. Since the total mass of an SIE lens is infinite, the question
needs to be redefined, so we ask about the mass within some aperture of finite
area. For an SIE, the mass (in dimensionless units) within the critical
ellipse is simply $b^2$.
